Illumination Level Independence in the Dynamic Laser Speckle Analysis

### 2018-10-24 article/article_1.tex
Modificando titulo
Corrigindo texto e refrencias

\title{Towards Illumination Level Independence in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{-------- ------- ------}
\author{-------- ------- ------}

% \author{Fernando Pujaico Rivera\fnref{myfootnote2}}
% \author{Roberto Alves Braga Jr.\fnref{myfootnote1}}
% \address{University Federal of Lavras, Lavras, Brazil}
% \fntext[myfootnote2]{201518201@posgrad.ufla.br}
% \fntext[myfootnote1]{robertobraga@deg.ufla.br }

@@

\begin{keyword}
Biospeckle laser \sep 
Biospeckle index \sep 
Biospeckle signal\sep 
Biological activity \sep
Dynamic speckle \sep  
Backscattering.
\end{keyword}

@@

\subsection{Data packages of drying ink}
\label{sec:descriptionink}
Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
a red laser was pointed to a layer of drying ink monitored by a digital camera;
the images are collected receiving two different illumination levels, because of the neutral 
density lens covering partially the laser beam \cite{REIS2016}.
The images were placed in data packages and
are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with the two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
\label{fig:system}
\end{figure}
In each image of the packages were selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with red lines in the Fig. \ref{fig:regions}. In the right side of the Fig. \ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}
%\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\

@@

We have in the drying ink regions  with
two levels of illumination; thus, we  separated each package in two sub package
(left and right), representing each one of the regions shown in the Fig. \ref{fig:regions}.
These sub-packages were filtered,
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, that was used to obtain
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data packages.}
\label{fig:filtering}
\end{figure}

the temporal speckle deviation matrix and the 
temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$.

@@

In this work were presented comparisons between the values of the temporal speckle 
deviation index to three different frequency bands of the speckle signal and
different illuminations levels, in a
dynamic laser speckle analysis. The results showed that the influence of the illumination level in
the DLSI index decreases with the use of signals with high frequency bands.

>>>>

\title{Illumination Level Independence in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

% Group authors per affiliation:
\author{Fernando Pujaico Rivera}
\author{Roberto Alves Braga Jr.}

\address{University Federal of Lavras, Lavras, Brazil}
\fntext[myfootnote2]{201518201@posgrad.ufla.br}
\fntext[myfootnote1]{robertobraga@deg.ufla.br }
%

@@

\begin{keyword}
Biospeckle laser \sep 
Biospeckle index \sep 
Biospeckle signal\sep 
Biological activity \sep
Dynamic speckle 
\end{keyword}

@@

\subsection{Data packages of drying ink}
\label{sec:descriptionink}
Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
a red laser was pointed to a layer of drying ink monitored by a digital camera;
the images are collected receiving two different illumination levels, because of the neutral 
density lens covering partially the laser beam \cite{REIS2016}.
The images were placed in data packages and
are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with the two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
\label{fig:system}
\end{figure}
In each image of the packages were selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with red lines in the Fig. \ref{fig:regions}; thus, in the right side of the Fig. \ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}
%\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\

@@

We have in the drying ink regions
two levels of illumination; thus, we  separated each package in two sub package
(left and right), representing each one of the regions shown in the Fig. \ref{fig:regions}.
These sub-packages were filtered,
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, that was used to obtain
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data packages.}
\label{fig:filtering}
\end{figure}
the temporal speckle deviation matrix and the 
temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$.

@@

In this work were presented comparisons between the values of the temporal speckle 
deviation index to three different frequency bands of the speckle signal and
different illuminations levels, in a
dynamic laser speckle analysis. The results showed that the influence of the illumination level in
the DLSI index, like the temporal speckle deviation 
index, decreases with the use of signals with high frequency bands.
